Pillar 1 - Sequential Pattern Mining

### 2019-03-13 Pillar 1 - Sequential Pattern Mining.Rmd
compute item_g var in d_transactions$G

@@

## Transactions
```{r making transactions, cache = TRUE}
make_transaction <- function(data = d_transactions$taken_PF_HL, item = item){

  data %>%
    group_by(
      sequenceID
    ) %>%
    summarise(
      list_item = list(unique(!!enquo(item)))
    ) %>%
    ungroup %>%
    pull(
      list_item
      ) %>%
    as("transactions")

@@

#
# Making transactions
transactions <- list()

transactions$taken <- make_transaction(item = item   )
transactions$PF    <- make_transaction(item = item_PF)
transactions$HL    <- make_transaction(item = item_HL)
transactions$TPF   <- make_transaction(data = d_transactions$T_PF_HL, item = item_TPF)
transactions$THL   <- make_transaction(data = d_transactions$T_PF_HL, item = item_THL)
transactions$G     <- make_transaction(data = d_transactions$G  , item = item_G  )

# inspect(head(transactions$taken, 10))
```

>>>>

  mutate(item_g = paste_(item, grade_ceil)) %>%

@@

## Transactions
```{r making transactions, cache = TRUE}
make_transaction <- function(data, item){

    group_by(sequenceID) %>%
    summarise(list_item = list(unique(!!item))) %>%
    ungroup %>%

    pull(list_item) %>%

    as("transactions")

@@

transactions <- tribble(
  ~ ID   ,  ~ data                    , ~ item,
  "taken", d_transactions$taken_PF_HL, quo(item),
  "PF"   , d_transactions$taken_PF_HL, quo(item_PF),
  "HL"   , d_transactions$taken_PF_HL, quo(item_HL),
  "TPF"  , d_transactions$T_PF_HL    , quo(item_TPF),
  "THL"  , d_transactions$T_PF_HL    , quo(item_TPF),
  "G"    , d_transactions$G          , quo(item_g)
  ) %>%

  mutate(transactions = list(data, item) %>% pmap(make_transaction))

inspect(head(transactions$transactions[[2]], 10))
```
